Reproducibility of HCP pipelines across operating systems

### 2017-06-22 paper.tex
Ack
Added os and hcp details

\section{Materials and Methods}
\begin{itemize}
  \item{verifyFiles Script}
  \item{Input parameters}
  \item{Working}
  \item{Reference File}
  \item{SQLite}
  \item{Reprozip}
  \item{Query to find out the process that created a particular file}
  \item{Ignored files}
  \item{checksums-before-after}
  \item{monitor.txt}
  \item{metrices}
  \item{Describe how the reference file was processed,"docker run -it --rm --security-opt seccomp=unconfined -w /data -v /home/lscaria/BigDataLab:/data 8eeec0517441 /bin/bash"}
  \item{hardware-monitor metric}
  \item{Distance using fslmats,nibabel}
  \item{corruption check flag}
\end{itemize}
\subsection{Dataset}

@@

CBRAIN team. Compute Canada.

>>>>

\section{Materials and Methods}
\begin{itemize}
\subsection{Operating System and Applications} 
Since we are conducting a study on the influence of the changes in operating system and the underlying libraries on the biological images,we chose different versions of CentOS. CentOS is a community-driven  free software effort focused on delivering a roubust open source ecosystem. CentOS focuses on development of framework for cloud providers, the hosting community, and scientific data processing.\cite{https://www.centos.org/about/} The different versions chosen we selected for our study are centos5.11, centos6.8 and centos7.2.1511. These images are available in the official centos \url{https://hub.docker.com/\_/centos/} docker repository.

These operating system versions are base images. A base image is the image that is used to create all of your container images\url{https://www.ibm.com/support/knowledgecenter/en/SS6PEW\_9.5.0/com.ibm.help.install.omsoftware.doc/installation/c\_DockerBaseImage.html}. On top of the base images, the required software libraries were installed to create containers having all the required prerequisites and softwares.

Human Connectome Project\cite{The WU-Minn Human Connectome Project: An Overview} is a consortium led by Washington University, University of Minnesota, and Oxford University is undertaking a systematic effort to map macroscopic human brain circuits and their relationship to behavior in a large population of healthy adults.

  \item{verifyFiles Script}
  \item{Input parameters}
  \item{Working}
  \item{Reference File}
  \item{SQLite}
  \item{Reprozip}
  \item{Query to find out the process that created a particular file}
  \item{Ignored files}
  \item{checksums-before-after}
  \item{monitor.txt}
  \item{Metrices}
  \item{Describe how the reference file was processed,"docker run -it --rm --security-opt seccomp=unconfined -w /data -v /home/lscaria/BigDataLab:/data 8eeec0517441 /bin/bash"}
  \item{Hardware-monitor metric}
  \item{Distance using fslmats,nibabel}
  \item{Corruption check flag}
\end{itemize}
\subsection{Dataset}

@@

CBRAIN team. Compute Canada(Calcul Quebec).
